### 2020-05-25 writeup/proof_taskonomy.tex
clarify

We study the transfer function of taskonomy \cite{ZSSGM18}.
The algorithm is as follows.
First, we obtain the single-task estimator $\hat{\beta}_i$ from every task, for $1\le i \le k$.
This forms the shared representation $B$ in Algorithm \ref{alg_estimator}.
Then, we learn the output layer on the target task by solving equation \eqref{eq_mtl}.
We use our tools to compare the estimator of this setting to single-task learning.

>>>>

We study the transfer function of taskonomy \cite{ZSSGM18}.
The algorithm is as follows.
First, we obtain the single-task estimator $\hat{\beta}_i$ from every task, for $1\le i \le k$.
This forms the shared representation $B = [\hat{\beta}_1,\hat{\beta}_2,\dots,\hat{\beta}_{k-1}]$.
Then, we learn the output layer $W_k$ on the target task by solving equation:
\begin{align}
	\bignorm{X_k B W_k - Y_k}^2
\end{align}
After getting $W_k$, we use $B W_k$ as estimator and $\te(B W_k)$ is the test error of the estimator
We use our tools to compare $\te(B W_k)$ to $\te(\beta_k^{\STL})$.
